On existence of integral point sets and their diameter bounds \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2020-01-02 pps-linear-bound/pps-linear-lower-bound.tex
[J220] Proof on Lemma 4.2 (ex Lemma 2.6)
See Review 2, medium remark 5

\begin{lemma}
	\label{lem:intervals_cross}
	If open line segments $M_1 M_2$ and $M_3 M_4$ do not intersect,
	%$M_1 \neq M_2$, $M_3 \neq M_4$,
	then the set $cr(M_1,M_2) \cap cr(M_3,M_4)$ is either a straight line or contains 2 or 4 points.
\end{lemma}
It is important that we consider the intersection of open line segments,
so e.g. the cases $M_1 = M_3$ and $M_3 \in M_1 M_2$ satisfy the conditions of Lemma~\ref{lem:intervals_cross}.

>>>>

\begin{lemma}
	\label{lem:intervals_cross}
	If open line segments $M_1 M_2$ and $M_3 M_4$ do not intersect,
	%$M_1 \neq M_2$, $M_3 \neq M_4$,
	then the set $cr(M_1,M_2) \cap cr(M_3,M_4)$ is either a straight line or contains 2 or 4 points.
\end{lemma}

\begin{proof}
	Consider straight lines $l^1_1$, $l^1_2$, $l^2_1$, $l^2_2$
	such that $cr(M_1,M_2) = l^1_1 \cup l^1_2$ and $cr(M_3,M_4) = l^2_1 \cup l^2_2$.

	The cases $l^1_1 = l^2_1$, $l^1_2 = l^2_2$ and $l^1_1 = l^2_2$, $l^1_2 = l^2_1$ are impossible,
	because the centers of open line segments $M_1 M_2$ and $M_3 M_4$ do not coincide as far as
	the open line segments do not intersect.
	So, all the possible cases (up to enumeration of the straight lines) are:
	\begin{itemize}
		\item
			$l^1_1 = l^2_1$, $l^1_2 \neq l^2_2$.
			The straight lines $l^1_2$ and $l^2_2$ are both orthogonal to $l^1_1$ and thus do not intersect;
			thus, $cr(M_1,M_2) \cap cr(M_3,M_4) = l^1_1 = l^2_1$.
		\item
			$l^1_1$ is parallel to $l^2_1$ and $l^1_2$ is parallel to $l^2_2$.
			Then
			\begin{equation*}
				cr(M_1,M_2) \cap cr(M_3,M_4) = (l^1_1 \cup l^1_2)\cap(l^2_1 \cup l^2_2) =
				\\=
				(l^1_1 \cap l^2_2) \cup (l^1_2 \cap l^2_1)
				,
			\end{equation*}
			that is two points.
		\item
			$l^1_1$ is neither parallel nor orthogonal to $l^2_1$.
			Then the intersection contains 4 points.
	\end{itemize}
\end{proof}

\begin{remark}
	It is important that we consider the intersection of open line segments in the claim of Lemma~\ref{lem:intervals_cross},
	so e.g. the cases $M_1 = M_3$ and $M_3 \in M_1 M_2$ satisfy the conditions of Lemma~\ref{lem:intervals_cross}.
\end{remark}
